---
title: |-
  <b>**Subject**:</b> Statistical Review of P180001
  <b>&emsp;&emsp;&emsp;&nbsp;&nbsp;</b> Device for treatment of insanity in FDA reviewers, Pain Inc.
subtitle: |-
  <b>**To**:&emsp;&emsp;</b>  Slave Driver, Lead Reviewer 
  <b>&emsp;&emsp;&emsp;&nbsp;&nbsp;</b>  ODE/SOS/ZZZ
author: |-
  <b>**From**:&emsp;&nbsp;Mathematical Statistician:</b>  Laura Thompson, Ph.D. 
  <b>&emsp;&emsp;&emsp;&nbsp;&nbsp;&nbsp;</b>  OSB/DBS/TSBII
date: <b>**Date**:&emsp;&nbsp;</b> `r format(Sys.time(), '%B %d, %Y')`
output:
  word_document:
    reference_docx: word-styles-reference-03.docx
    md_extensions: +styles+empty_paragraphs+all_symbols_escapable+hard_line_breaks
css: word.css
---

<br />

```{r setup, warning=FALSE, echo=FALSE}

# load packages
library(MASS)
require(knitr, quietly = TRUE)

# set global options for R chunks
opts_chunk$set(warning=FALSE, message=FALSE, echo=FALSE, cache=TRUE, cache.extra=list(R.version))


```


# Background

This describes the background of the device, including regulatory history and device description.


# Study Design

The study was a randomized, controlled, two-arm trial.  Here are some other details about the study.


## Primary Endpoints

The primary effectiveness endpoint was the subject's score on the Happiness Index.


## Secondary Endpoints

The secondary endpoints were  

- Endpoint 1
- Endpoint 2
- Endpoint 3


# Study Results

Results showed that the device was not effective.


# Statistical Issues

This section describes my issues with the sponsor's analyses..



## Issue 1

Here is the first issue with the sponsor's analyses.

```{r primaryEffAnalysis}
# Here is my analysis of the primary endpoint
# R code goes here.  The output will show up in the word document. 

```

## Issue 2

Here is the second issue.


# Deficiencies

1. Def 1
2. Def 2


# Conclusions

In this paragraph, I describe my conclusions.

<!--<br /> is for a line break -->
<br />

If you have questions about this review, please contact me.

#### Laura Thompson


<!--[Laura Thompson]{custom-style="rightjustify"}-->

<!--<div style="rightjustify">
Laura
</div>-->


